Improving real-time trend estimates using local parametrisation of polynomial regression filters

### 2024-04-21 paper/article_jos.tex
update nn + correction local param h<6 + imports errors

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Improving real-time trend estimates using local parametrisation of local polynomial regression filters},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Improving real-time trend estimates using local parametrisation
of local polynomial regression filters}
\author{}
\date{}

@@

This paper studies and compares real-time estimates of the trend cycle
component with moving averages based on local polynomial regression. In
particular, this theory allows to reproduce Henderson's symmetric and
Musgrave's asymmetric filters. This paper describes how they can be
extended to include a timeliness criterion to minimise the phase shift.
While asymmetric filters are generally parameterised globally, which can
be suboptimal around turning points, this paper proposes a procedure for
parameterising them locally. An empirical comparison, based on simulated
and real data, shows that modelling polynomial trends that are too
complex introduces more revisions without reducing the phase shift, and
that local parameterisation reduces the delay in detecting turning
points and reduces revisions. The paper also shows how these results can
be easily reproduced using the R package \texttt{rjd3filters} dedicated
to the manipulation of moving averages.

@@

A moving average, or linear filter, is a statistical method that
consists in applying a rolling weighted mean to a times series: for each
date \(t\) it computes a weighted mean of \(p\) past points and \(q\)
future points where \(p,q\geq0\) depends on the moving average. Moving
averages are ubiquitous in business cycle extraction and seasonal
adjustment methods. For example, the X-13ARIMA seasonal adjustment
method uses several moving averages to estimate the main components of a
time series. Symmetric filters are applied to the center of the series,
but when it comes to estimate the most recent points, all of these
methods must rely on asymmetric filters. For trend-cycle extraction, the
most popular symmetric filter is the \textcite{henderson1916note} moving
average, which is used in the X-13ARIMA seasonal adjustment algorithm.

However, for real-time estimates, due to the lack of future
observations, all these methods must rely on asymmetric filters to
estimate the most recent points. For example, for trend-cycle
extraction, X-13ARIMA uses Henderson's symmetric filter and
\textcite{musgrave1964set}'s asymmetric filters on an extended series
using an ARIMA model. Since the predicted values are linear combinations
of past values, this amounts to applying asymmetric averages at the end
of the series.

@@

Using local polynomial regression, \textcite{proietti2008} developed
general class of symmetric and asymmetric moving averages. In
particular, it makes possible to reproduce Henderson's symmetric filter
and Musgrave's asymmetric filters. However, these methods have two
drawbacks. Firstly, the phase shift (i.e.~the delay in detecting turning
points) is not directly controlled. Secondly, asymmetric filters depend
on a parameter that is generally estimated over the whole series using
assumptions that may be wrong locally. The aim of this study is to
propose extensions to the \textcite{proietti2008} class of filters in
order to take these shortcomings into account. The extensions have been
implemented in the R \texttt{rjd3filters} package (available at
\url{https://github.com/rjdemetra/rjd3filters}) and are therefore easily
reusable.

In Section~\ref{sec-propMM}, we describe the general properties of
moving averages and the associated quality criteria. This allows us to
understand the foundations behind the construction of moving averages
from local polynomial regressions, as well as those behind the two
extensions proposed in this article (Section~\ref{sec-nonparamreg}). In
a final section (Section~\ref{sec-comparison}), all these methods are
compared empirically on simulated and real series.

\section{Some properties on moving averages}\label{sec-propMM}

Lots of papers describe the definition and the properties of moving
averages and linear filters, see for example \textcite{ch12HBSA}. In
this section we summarize some of the main results to understand the
next sections.

Let \(p\) et \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) or \(M\) is defined by a set of coefficients
\(\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}\)
such as for all time series \(X_t\): \[
M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

@@

To interpret the notions of gain and phase shift, it is useful to
illustrate the effects of moving averages on harmonic series
\(X_t=\e^{-i\omega t}\) with \(\omega\in[0,\pi]\). The moving average
\(M_{\boldsymbol\theta}\) transforms \(X_t\) into: \[
Y_t = M_{\boldsymbol\theta}X_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot X_t.
\] The function
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}\)
is called the \emph{transfer function} or \emph{frequency response
function}. The frequency response function can equivalently be defined
as
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}\)
ou
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}\).
It can be rewritten as: \[
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
\] where
\(\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert\)
is the \emph{gain} or \emph{amplitude} function and
\(\varphi_{\boldsymbol\theta}(\omega)\) is the \emph{phase shift} or
\emph{time shift} function. This function is sometimes represented as
\(\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}\)
to mesure the phase shift in number of periods. For all symmetric moving
average we have
\(\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})\).

@@

Fourier decomposition allows to analyze any time series as a sum of
harmonic series, and each component (trend, cycle, seasonal, irregular)
is associated with a set of frequencies. Noting \(\omega = 2\pi/p\), the
harmonic series of frequency \(\omega\) represents a series that repeats
itself every \(p\) periods. For example, for a monthly series (12
observations per year), seasonal movements are those that repeat every
year: they are therefore associated with frequencies \(2\pi/12\) (annual
periodicity), \(2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5\). In this
paper, we consider that the trend-cycle is associated with frequencies
in the interval \([0, 2\pi/12[\), i.e.~movements recurring at least
every 12 months. Even if different frequencies are sometimes used
(e.g.~\([0, 2\pi/36]\) to consider only cycles of at least 36 months),
this has no impact on the results of the study. The other frequencies,
\([2\pi/12, \pi]\) are associated with the irregular component
(undesirable oscillations).

Figure~\ref{fig-graphsmusgrave} shows the gain and phase shift function
for the asymmetric Musgrave filter (see Section~\ref{sec-lppasymf})
often used for real-time trend-cycle estimation (i.e.~when no point in
the future is known). The gain function is greater than 1 on the
frequencies associated with the trend-cycle (\([0, 2\pi/12]\)): this
means that the trend-cycle is well preserved and that short cycles of 1
to 2 years (\([2\pi/24,2\pi/12]\)) are even amplified. However, cycles
of 8 to 12 months (\([2\pi/12, 2\pi/8]\)), considered undesirable
because associated with the irregular, are also amplified: this can lead
to the detection of false turning points. At other frequencies, the gain
function is less than 1, but always positive: this means that the series
smoothed by this moving average will always contain noise, even if it is
attenuated. Analysis of the phase shift shows that the shorter the
cycles, the greater the phase shift: this means that on series smoothed
by this moving average, turning points could be detected at the wrong
date.

@@

Trend-cycles are generally modelled by local polynomial trends (see
Section~\ref{sec-nonparamreg}). In order to best preserve the
trend-cycles, we try to have moving averages that preserve the
polynomial trends. A moving average \(M_{\boldsymbol\theta}\) preserves
a function of time \(f(t)\) if
\(\forall t:M_{\boldsymbol\theta} f(t)=f(t)\).

We have the following properties for the moving average
\(M_{\boldsymbol\theta}\):

\begin{itemize}
\item
  To preserve a constant trend \(X_t=a\) we need: \[
  \forall t:M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}=\sum_{k=-p}^{+f}\theta_ka=a\sum_{k=-p}^{+f}\theta_k=a.
  \] The sum of the coefficients of the moving average
  \(\sum_{k=-p}^{+f}\theta_k\) must then be equal to \(1\).
\item
  To preserve linear trends \(X_t=at+b\) we need: \[
  \forall t:\:M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}=\sum_{k=-p}^{+f}\theta_k[a(t+k)+b]=a\sum_{k=-p}^{+f}k\theta_k+(at+b)\sum_{k=-p}^{+f}\theta_k=at+b.
  \] Which is equivalent to: \[
  \sum_{k=-p}^{+f}\theta_k=1
  \quad\text{et}\quad
  \sum_{k=-p}^{+f}k\theta_k=0.
  \]
\item
  In general, \(M_{\boldsymbol\theta}\) preserves polynomials of degree
  \(d\) if and only if: \[
  \sum_{k=-p}^{+f}\theta_k=1
   \text{ and }
  \forall j \in \left\llbracket 1,d\right\rrbracket:\:
  \sum_{k=-p}^{+f}k^j\theta_k=0.
  \]
\item
  If \(M_{\boldsymbol\theta}\) is symmetric (\(p=f\) and
  \(\theta_{-k} = \theta_k\)) and preserves polynomials of degree \(2d\)
  then it also preserves polynomials of degree \(2d+1\).
\end{itemize}

@@

Indeed, let \(\{\varepsilon_t\}\) a sequence of independent random
variables with \(\E{\varepsilon_t}=0\), \(\V{\varepsilon_t}=\sigma^2\):
\[
\V{M_{\boldsymbol\theta}\varepsilon_t}=\V{\sum_{k=-p}^{+f} \theta_k \varepsilon_{t+k}}
= \sum_{k=-p}^{+f} \theta_k^2 \V{\varepsilon_{t+k}}=
\sigma^2\sum_{k=-p}^{+f} \theta_k^2.
\]

@@

For symmetric filters, the phase shift function is equal to zero (modulo
\(\pi\)). So there is no delay in detecting turning points. However,
they cannot be used in the beginning and in the end of the time series
because no past or future value can be used. Thus, for real-time
estimation, it is needed to build asymmetric moving average that
approximate the symmetric moving average.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Use asymmetric moving averages to take account of the lack of
  available data;
\item
  Apply symmetrical filters to extended forecast series. This method
  seems to date back to \textcite{deforest1877adjustment}, which also
  suggests modelling a polynomial trend of degree three or less at the
  end of the period:\\
  ``\emph{As the first \(m\) and last \(m\) terms of the series cannot
  be reached directly by the formula, the series should be graphically
  extended by m terms at both ends, first plotting the observations on
  paper as ordinates, and then extending the curve along what seems to
  be its probable course, and measuring the ordinates of the extended
  portions.} \emph{It is not necessary that this extension should
  coincide with what would be the true course of the curve in those
  parts. } \emph{The important point is that the m terms thus added,
  taken together with the \(m+1\) adjacent given terms, should follow a
  curve whose form is approximately algebraic and of a degree not higher
  than the third.}''\\
  This is also the approach used in the X-13ARIMA seasonal adjustment
  method, which extends which extends the series by one year with an
  ARIMA model.
\end{enumerate}

@@

Conversely, the implicit forecasts of an asymmetric moving average can
be deduced from a reference symmetric moving average. This allows to
judge the quality of real-time estimates of the trend-cycle and to
anticipate future revisions when forecasts are far from expected
evolutions.\\
Let us denote \(v=(v_{-h},\dots, v_{h})\) the reference symmetrical
moving average and \(w^0,\dots w^{h-1}\) a sequence of asymmetrical
moving averages, of order \(h+1\) to \(2h\) used to estimate the last
\(h\) points with, for convention, \(w_t^q=0\) for \(t>q\). This means
that \(w^0=(w_{-h}^0,\dots, w_{0}^0)\) is used for estimation in real
time (when no points are known in the future),
\(w^1=(w_{-h}^1,\dots, w_{1}^1)\) for estimation of the penultimate
point (when only one point is known in the future), and so on. Let also
note \(y_{-h},\dots,y_{0}\) the observed series studied and
\(y_{1}^*,\dots y_h^*\) the implicit forecast induced by
\(w^0,\dots w^{h-1}\). This means that for all \(q\) we have: \[
\forall q, \quad \underbrace{\sum_{i=-h}^0 v_iy_i + \sum_{i=1}^h v_iy_i^*}_{\text{smoothing by }v\text{ of the extended series}}
=\underbrace{\sum_{i=-h}^0 w_i^qy_i + \sum_{i=1}^h w_i^qy_i^*}_{\text{smoothing by }w^q\text{ of the extended series}}.
\] This is equivalent to: \[
\forall q, \quad \sum_{i=1}^h (v_i- w_i^q) y_i^*
=\sum_{i=-h}^0 (w_i^q-v_i)y_i.
\] To sum up, in matrix form, this is equivalent to solving: \[
\scriptstyle
\begin{pmatrix}
  v_1 & v_2 & \cdots & v_h \\
  v_1 - w_1^1 & v_2 & \cdots & v_h \\
  \vdots & \vdots & \cdots & \vdots \\
   v_1 - w_1^{h-1} & v_2-w_2^{h-1} & \cdots & v_h
\end{pmatrix}
\begin{pmatrix}y_1^* \\ \vdots \\ y_h^*\end{pmatrix}=
\begin{pmatrix}
  w_{-h}^0 - v_{-h} & w_{-(h-1)}^0 - v_{-(h-1)} & \cdots & w_{0}^0 - v_{0} \\
  w_{-h}^1 - v_{-h} & w_{-(h-1)}^1 - v_{-(h-1)} & \cdots & w_{0}^1 - v_{0} \\
  \vdots & \vdots & \cdots & \vdots \\
  w_{-h}^{h-1} - v_{-h} & w_{-(h-1)}^{h-1} - v_{-(h-1)} & \cdots & w_{0}^{h-1} - v_{0}
\end{pmatrix}
\begin{pmatrix}y_{-h} \\ \vdots \\ y_0\end{pmatrix}.
\] This is implemented in the \texttt{rjd3filters::implicit\_forecast()}
function.

@@

\subsubsection{Quality indicators for asymmetric moving
averages}\label{subsec:crit-qual}

For asymmetric filters, most of the criteria come from those defined by
\textcite{ch15HBSA} and \textcite{trilemmaWMR2019} to build asymmetric
filters. They are summarised in Table~\ref{tab-QC} and can be calculated
using the \texttt{rjd3filters::diagnostic\_matrix()} function.

\textcite{ch15HBSA} propose a general approach to derive linear filters,
based on an optimisation problem involving three criteria:
\emph{Fidelity} (\(F_g\)), \emph{Smoothness} (\(S_g\)) and
\emph{Timeliness} (\(T_g\)). Fidelity can be directly linked to the
reduction in variance created by the filter, and timeliness to the
notion of phase shift, which again we want to be low. This method can be
used inR with the function \texttt{rjd3filters::fst\_filter()}.

\textcite{trilemmaWMR2019} propose an approach based on the
decomposition of the mean squared error between the symmetric and the
asymmetric filter in four quantities: \emph{Accuracy} (\(A_w\)),
\emph{Timeliness} (\(T_w\)), \emph{Smoothness} (\(S_w\)) and
\emph{Residual} (\(R_w\)). A simplified version of this method can be
used in R with the function \texttt{rjd3filters::dfa\_filter()}.

\caption{\label{tab-QC} Quality criteria for asymmetric filters ($q=0,1,2$) computed by local polynomials using the Henderson kernel with $h=6$ and $R=3,5$.}

>>>>

@@

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Improving real-time trend estimates using local parametrisation of polynomial regression filters},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Improving real-time trend estimates using local parametrisation
of polynomial regression filters}
\author{}
\date{}

@@

This paper studies and compares real-time estimates of the trend-cycle
component with moving averages based on local polynomial regression. In
particular, this theory allows us to reproduce Henderson's symmetric and
Musgrave's asymmetric filters. This paper describes how they can be
extended to include a timeliness criterion to minimise the phase shift.
While asymmetric filters are generally parametrised globally, which can
be suboptimal around turning points, this paper proposes a procedure for
parametrising them locally. An empirical comparison, based on simulated
and real data, shows that modelling polynomial trends that are too
complex introduces more revisions without reducing the phase shift, and
that local parametrisation reduces the delay in detecting turning points
and reduces revisions. The paper also shows how these results can be
easily reproduced using the R package \texttt{rjd3filters} dedicated to
the manipulation of moving averages.

@@

A moving average, or linear filter, is a statistical method that
consists of applying a rolling weighted mean to a times series: for each
date \(t\) it computes a weighted mean of \(p\) past points and \(q\)
future points where \(p,q\geq0\) depends on the moving average. Moving
averages are ubiquitous in business cycle extraction and seasonal
adjustment methods. For example, the X-11 decomposition method
\autocite{x11}, used in X-13ARIMA-SEATS software \autocite{x13}, uses
several moving averages to estimate the main components of a time
series. Symmetric filters are applied to the center of the series, but
when it comes to estimate the most recent points, all of these methods
must rely on asymmetric filters. For trend-cycle extraction, the most
popular symmetric filter is the \textcite{henderson1916note} moving
average, which is used in the X-11 seasonal adjustment algorithm.

However, for real-time estimates, due to the lack of future
observations, all these methods must rely on asymmetric filters to
estimate the most recent points. For example, for trend-cycle
extraction, X-11 uses Henderson's symmetric filter and
\textcite{musgrave1964set}'s asymmetric filters on an extended series
using an ARIMA model. Since the predicted values are linear combinations
of past values, this amounts to applying asymmetric averages at the end
of the series.

@@

Using local polynomial regression, \textcite{proietti2008} developed a
general class of symmetric and asymmetric moving averages. In
particular, it becomes possible to reproduce Henderson's symmetric
filter and Musgrave's asymmetric filters. However, these methods have
two drawbacks. Firstly, the phase shift (i.e.~the delay in detecting
turning points) is not directly controlled. Secondly, asymmetric filters
depend on a parameter that is generally estimated over the whole series
using assumptions that may be wrong locally. The aim of this study is to
propose extensions to the \textcite{proietti2008} class of filters in
order to take these shortcomings into account. The extensions have been
implemented in the statistical software R \autocite{logicielr}
\texttt{rjd3filters} package (available at
\url{https://github.com/rjdemetra/rjd3filters}) and can therefore be
easily used.

In section~\ref{sec-propMM}, we describe the general properties of
moving averages and the associated quality criteria. This allows us to
understand the foundations behind the construction of moving averages
from local polynomial regressions, as well as those behind the two
extensions proposed in this article (section~\ref{sec-nonparamreg}). In
a final section (section~\ref{sec-comparison}), all these methods are
compared empirically on simulated and real series.

\section{Some properties of moving averages}\label{sec-propMM}

Numerous papers describe the definition and the properties of moving
averages and linear filters, see for example \textcite{ch12HBSA}. In
this section we summarize some of the main results to understand the
next sections.

Let \(p\) and \(f\) two integers, a moving average
\(M_{\boldsymbol\theta}\) or \(M\) is defined by a set of coefficients
\(\boldsymbol\theta=\transp{\begin{pmatrix}\theta_{-p}&\cdots&\theta_{f}\end{pmatrix}}\)
such as for all time series \(X_t\): \[
M_{\boldsymbol\theta}(X_t)=\sum_{k=-p}^{+f}\theta_kX_{t+k}.
\]

@@

To interpret the notions of gain and phase shift, it is useful to
illustrate the effects of moving averages on harmonic series
\(X_t=\e^{-i\omega t}\) with \(\omega\in[0,\pi]\). The moving average
\(M_{\boldsymbol\theta}\) transforms \(X_t\) into: \[
Y_t = M_{\boldsymbol\theta}X_t = \sum_{k=-p}^{+f} \theta_k \e^{-i \omega (t+k)}
= \left(\sum_{k=-p}^{+f} \theta_k \e^{-i \omega k}\right)\cdot X_t.
\] The function
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{-i \omega k}\)
is called the \emph{transfer function} or \emph{frequency response
function}. The frequency response function can alternatively be defined
as
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{i \omega k}\)
or
\(\Gamma_{\boldsymbol\theta}(\omega)=\sum_{k=-p}^{+f} \theta_k e^{2\pi i \omega k}\).
It can be rewritten as: \[
\Gamma_{\boldsymbol\theta}(\omega) = \rho_{\boldsymbol\theta}(\omega)\e^{i\varphi_{\boldsymbol\theta}(\omega)},
\] where
\(\rho_{\boldsymbol\theta}(\omega)=G_{\boldsymbol\theta}(\omega)=\lvert\Gamma_{\boldsymbol\theta}(\omega)\rvert\)
is the \emph{gain} or \emph{amplitude} function and
\(\varphi_{\boldsymbol\theta}(\omega)\) is the \emph{phase shift} or
\emph{time shift} function. We this have: \begin{align*}
\rho_{\boldsymbol\theta}(\omega) &=\sqrt{\left(\sum_{k=-p}^{+f}\theta_k\cos(\omega k)\right)^2+
\left(\sum_{k=-p}^{+f}\theta_k\sin(\omega k)\right)^2} \\
\tan \varphi_{\boldsymbol\theta}(\omega) &=- \frac{\sum_{k=-p}^{+f}\theta_k\sin(\omega k)}{\sum_{k=-p}^{+f}\theta_k\cos(\omega k)} \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) \ne 0 \\
&= 0 \text{ if }\sum_{k=-p}^{+f}\theta_k\cos(\omega k) = 0.
\end{align*} The phase shift is sometimes represented as
\(\phi_{\boldsymbol\theta}(\omega)=\frac{\varphi_{\boldsymbol\theta}(\omega)}{\omega}\)
to measure it in number of periods. For all symmetric moving averages we
have \(\varphi_{\boldsymbol\theta}(\omega)\equiv 0 \;(modulo\;{\pi})\).

@@

Fourier decomposition allows us to analyze any time series as a sum of
harmonic series, and each component (trend, cycle, seasonal, irregular)
is associated with a set of frequencies. Noting \(\omega = 2\pi/s\), the
harmonic series of frequency \(\omega\) represents a series that repeats
itself every \(s\) periods. For example, for a monthly series (\(s=12\)
observations per year), seasonal movements are those that repeat every
year: they are therefore associated with frequencies \(2\pi/12\) (annual
periodicity), \(2\pi/12\times 2=2\pi/6,\dots,2\pi/12\times 5\). In this
paper, we consider that the trend-cycle is associated with frequencies
in the interval \([0, 2\pi/12]\), i.e.~movements recurring at least
every 12 months. Even if different frequencies are sometimes used
(e.g.~\([0, 2\pi/36]\) to consider only cycles of at least 36 months),
this has no impact on the results of the study. The other frequencies,
\([2\pi/12, \pi]\) are associated with the irregular component
(undesirable oscillations).

figure~\ref{fig-graphsmusgrave} shows the gain and phase shift function
for the asymmetric Musgrave filter (see section~\ref{sec-lppasymf})
often used for real-time trend-cycle estimation (i.e.~when no point in
the future is known). The gain function is greater than 1 on the
frequencies associated with the trend-cycle (\([0, 2\pi/12]\)): this
means that the trend-cycle is well preserved and that short cycles of 1
to 2 years (\([2\pi/24,2\pi/12]\)) are even amplified. At other
frequencies, the gain function is less than 1, but always positive: this
means that the series smoothed by this moving average will always
contain noise, even if it is attenuated. Analysis of the phase shift
shows that the shorter the cycles, the greater the phase shift: this
means that on series smoothed by this moving average, turning points
could be detected at the wrong date.

@@

Trend-cycles are generally modelled by local polynomial trends (see
section~\ref{sec-nonparamreg}). In order to best preserve the
trend-cycles, we try to design moving averages that preserve the
polynomial trends. A moving average \(M_{\boldsymbol\theta}\) preserves
a function of time \(f(t)\) if
\(\forall t:M_{\boldsymbol\theta} f(t)=f(t)\).

For the moving average \(M_{\boldsymbol\theta}\), it can be shown that:

\begin{itemize}
\tightlist
\item
  \(M_{\boldsymbol\theta}\) preserves polynomials of degree \(d\) if and
  only if: \[
  \sum_{k=-p}^{+f}\theta_k=1
   \text{ and }
  \forall j \in \left\{1,2,\dots,d\right\}:\:
  \sum_{k=-p}^{+f}k^j\theta_k=0.
  \]
\item
  If \(M_{\boldsymbol\theta}\) is symmetric (\(p=f\) and
  \(\theta_{-k} = \theta_k\)) and preserves polynomials of degree \(2d\)
  then it also preserves polynomials of degree \(2d+1\).
\end{itemize}

@@

Indeed, let \(\{\varepsilon_t\}\) be a sequence of independent random
variables with \(\E{\varepsilon_t}=0\), \(\V{\varepsilon_t}=\sigma^2\):
\[
\V{M_{\boldsymbol\theta}\varepsilon_t}=\V{\sum_{k=-p}^{+f} \theta_k \varepsilon_{t+k}}
= \sum_{k=-p}^{+f} \theta_k^2 \V{\varepsilon_{t+k}}=
\sigma^2\sum_{k=-p}^{+f} \theta_k^2.
\]

@@

For symmetric filters, the phase shift function is equal to zero (modulo
\(\pi\)). So there is no delay in detecting turning points. However,
they cannot be used in the beginning and in the end of the time series
because no past or future value can be used. Thus, for real-time
estimation, it is needed to build asymmetric moving averages that
approximate the symmetric moving average.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Use asymmetric moving averages to take account of the lack of
  available data;
\item
  Apply symmetric filters to extended forecast series. This method seems
  to date back to \textcite{deforest1877adjustment}, which also suggests
  modelling a polynomial trend of degree three or less at the end of the
  period. A similar approach is used in the X-13ARIMA-SEATS seasonal
  adjustment method: the series is extend by one year (by default) with
  an ARIMA model to minimise the revisions associated to asymmetric
  filters
\end{enumerate}

@@

Conversely, the implicit forecasts of an asymmetric moving average can
be deduced from a reference symmetric moving average. This allows us to
judge the quality of real-time estimates of the trend-cycle and to
anticipate future revisions when forecasts are far from expected
evolutions.\\
Let us denote \(\boldsymbol v=(v_{-h},\dots, v_{h})\) the reference
symmetric moving average (used to compute the final estimates) and
\(\boldsymbol w^0,\dots, \boldsymbol w^{h-1}\) a sequence of asymmetric
moving averages used for the intermediate estimates.
\(\boldsymbol w^0=(w_{-h}^0, \dots, w_{0}^0)\) is used for estimation in
real time estimate (when 0 point in the future is known),
\(\boldsymbol w^1=(w_{-h}^1, \dots, w_{0}^1, w_{1}^1)\) is used for
estimation of the penultimate point (when only 1 in the future is
known), and so on. Let \(y_{t-h},\dots,y_{t}\) be the observed series
during the last \(h\) periods (for which asymmetric moving averages are
used to get the intermediate trend-cycle estimates for the dates \(t-h\)
to \(h\)). The implicit forecast \(y_{t+1}^*,\dots y_{t+h}^*\) induced
by \(w^0,\dots w^{h-1}\) are the forecasts of the series \(y_t\) for
which the estimates of the symmetric filter applied to the extended
series
\(\boldsymbol y^* = (y_{t-h}, \dots, y_t, y_{t+1}^*,\dots y_{t+h}^*)\)
produce the same estimates as the asymmetric filter applied to the
series \(\boldsymbol y^*\). This means: \begin{align*}
\underbrace{\sum_{i=-h}^0 v_iy_{ti} + \sum_{i=1}^h v_iy_{t+i}^*}_{\text{smoothing by }\boldsymbol v\text{ of the extended series}} &=
\underbrace{\sum_{i=-h}^0 w_i^0y_{t+i}}_{\text{smoothing by }\boldsymbol w^0\text{ using }0\text{ points after }t} \\
&=
\underbrace{\sum_{i=-h}^0 w_i^1y_{t+i} + w_1^1y_{t+1}^*}_{\text{smoothing by }\boldsymbol w^1\text{ using }1\text{ points after }t} \\
&= \underbrace{\sum_{i=-h}^0 w_i^2y_{t+i} + \sum_{i=1}{2}w_i^2y_{t+i}^*}_{\text{smoothing by }\boldsymbol w^2\text{ using }2\text{ points after }t} \\
&= \cdots \\
&=\underbrace{\sum_{i=-h}^0 w_i^{h-1}y_{t+i} + \sum_{i=1}^{h-1} w_i^{h-1}y_{t+i}^*}_{\text{smoothing by }\boldsymbol w^{h-1}\text{ using }h-1\text{ points after }t}
\end{align*} For any integer \(q\) between 0 and \(h-1\), using for
convention \(w_t^q=0\) if \(t>q\) we then have: \[
\sum_{i=1}^h (v_i- w_i^q) y_i^*
=\sum_{i=-h}^0 (w_i^q-v_i)y_i.
\] In matrix form, this is equivalent to solving: \[
\scriptstyle
\begin{pmatrix}
  v_1 & v_2 & \cdots & v_h \\
  v_1 - w_1^1 & v_2 & \cdots & v_h \\
  \vdots & \vdots & \cdots & \vdots \\
   v_1 - w_1^{h-1} & v_2-w_2^{h-1} & \cdots & v_h
\end{pmatrix}
\begin{pmatrix}y_1^* \\ \vdots \\ y_h^*\end{pmatrix}=
\begin{pmatrix}
  w_{-h}^0 - v_{-h} & w_{-(h-1)}^0 - v_{-(h-1)} & \cdots & w_{0}^0 - v_{0} \\
  w_{-h}^1 - v_{-h} & w_{-(h-1)}^1 - v_{-(h-1)} & \cdots & w_{0}^1 - v_{0} \\
  \vdots & \vdots & \cdots & \vdots \\
  w_{-h}^{h-1} - v_{-h} & w_{-(h-1)}^{h-1} - v_{-(h-1)} & \cdots & w_{0}^{h-1} - v_{0}
\end{pmatrix}
\begin{pmatrix}y_{-h} \\ \vdots \\ y_0\end{pmatrix}.
\] This is implemented in the \texttt{rjd3filters::implicit\_forecast()}
function.

@@
